The evolution of gene expression in the term placenta of viviparous mammals

### 2016-09-01 presentation/placenta_viviparous_presentation.Rnw
add egfr gene tree

>>>>

\begin{frame}{EGFR}
  \begin{figure}
<<egfr_expression,echo=FALSE,fig.width=5,fig.height=5>>=
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="EGFR" &
                                                    species=="homo sapiens"),
                                subtree=c("ENSG00000146648","ENSMODG00000009033"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees,
                                tree.line.width=2
                                )+
      geom_tiplab(size=5,color="black",fontface="italic")+xlim(0,0.4))

@ 
  \end{figure}
\end{frame}
